\Large Taking uncertainty seriously \newline \normalsize A Bayesian approach to word embedding bias estimation

### 2022-03-08 presentations/presentationBoston/presentationBoston.tex
presentation Boston added cosine etc.

  x11names, dvipsnames, bibspacing,natbib]{beamer}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias}{}
\begin{block}{Word embeddings}
\protect\hypertarget{word-embeddings}{}
\begin{itemize}
\item
  Representation of words with vectors of real numbers
\item
  Often built to predict the probability of co-occurence
\end{itemize}

\begin{longtable}[]{@{}llllll@{}}
\toprule
word & 1 & 2 & 3 & 4 & \ldots{} \\
\midrule
\endhead
woman & 0.456 & 0.267 & 0.675 & 0.131 & \ldots{} \\
man & 0.451 & 0.897 & 0.472 & 0.088 & \ldots{} \\
\bottomrule
\end{longtable}
\end{block}
\end{frame}

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-1}{}
\begin{block}{Cosine similarity \& distance}
\protect\hypertarget{cosine-similarity-distance}{}
\vspace{-4mm}

\begin{align} \tag{Sim}
\mathsf{cosineSimilarity}(A,B) & = \frac{A \cdot B}{\vert \vert A \vert \vert \,\vert \vert B \vert \vert}
\\
\tag{Distance}
\mathsf{cosineDistance}(A,B) &  = 1 - \mathsf{cosineSimilarity}(A,B)
\end{align}

\begin{itemize}
\item
  Geometric interpretation: direction (not length)
\item
  \(\mathsf{cosineDistance}\in (0, 2)\)
\item
  Naive interpretation: proximity corresponds to semantic similarity
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-2}{}
\begin{block}{The worry}
\protect\hypertarget{the-worry}{}
Word embeddings can learn implicit harmful biases

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-3}{}
\begin{block}{A visual example}
\protect\hypertarget{a-visual-example}{}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-4}{}
\begin{block}{Example: Word Embedding Association Test (WEAT)}
\protect\hypertarget{example-word-embedding-association-test-weat}{}
\vspace{1mm}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-5}{}
\begin{block}{Example: Word Embedding Association Test (WEAT)}
\protect\hypertarget{example-word-embedding-association-test-weat-1}{}
\begin{align*}
s(t,A,B) & = \frac{\sum_{a\in A}f(t,a)}{\vert A\vert} - \frac{\sum_{b\in B}f(t,b)}{\vert B\vert}
\\
WEAT(A,B) & = \frac{
\mu\left(\{s(x,A,B)\}_{x\in X}\right) -\mu\left(\{s(y,A,B)\}_{y\in Y}\right) 
}{
\sigma\left(\{s(w,A,B)\}_{w\in X\cup Y}\right)
}
\end{align*}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-6}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac}{}
\vspace{1mm}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-7}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac-1}{}
\begin{align*}
S(t_i, A_j) & = \frac{1}{\vert A_j\vert}\sum_{a\in A_j}\mathsf{cos}(t,a) \\
MAC(T,A) & = \frac{1}{\vert T \vert \,\vert A\vert}\sum_{t_i \in T }\sum_{A_j \in A} S(t_i,A_j)
\end{align*}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-8}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac-2}{}
\footnotesize 
\begin{table}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-9}{}
\begin{block}{Known challenges}
\protect\hypertarget{known-challenges}{}
\begin{itemize}
\tightlist
\item
  Gender-direction: insufficient indicator of bias
  \footnotesize  (\protect\hyperlink{ref-Gonen2019lipstick}{Gonen \&
  Goldberg, 2019})
\end{itemize}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems}{}
\begin{block}{Word list choice is unprincipled}
\protect\hypertarget{word-list-choice-is-unprincipled}{}
We run with it for comparison

@@

\begin{block}{No design considerations to sample size}
\protect\hypertarget{no-design-considerations-to-sample-size}{}
We statistically gauge the uncertainty that arises from raw sample sizes
\end{block}
\end{frame}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Outliers and surprisingly dissimilar words}
\protect\hypertarget{outliers-and-surprisingly-dissimilar-words}{}
We study those by visualizations and uncertainty estimates
\end{block}
\end{frame}

@@

\begin{block}{Our simulation}
\protect\hypertarget{our-simulation}{}
Suppose all similarities for two classes are randomly drawn from the
same distribution, \(\mathsf{Normal}(\mu = 0, \sigma = .05)\), you still
can get a really high WEAT!
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging}
\protect\hypertarget{the-problem-with-pre-averaging-1}{}
\begin{block}{One simulation}
\protect\hypertarget{one-simulation}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  Raw sd in data is 0.045
\item
  The sd of means is 0.023
\item
  The WEAT score is 1.825
\item
  The largest effect size reported by
  \protect\hyperlink{ref-Caliskan2017semanticsBiases}{Caliskan, Bryson,
  \& Narayanan}
  (\protect\hyperlink{ref-Caliskan2017semanticsBiases}{2017}) is 1.81!
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on real set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-real-set-up}{}
\begin{block}{One simulation on real set-up (no similarities and small
std)}
\protect\hypertarget{one-simulation-on-real-set-up-no-similarities-and-small-std}{}
\vspace{1mm}
\footnotesize

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-8-1} \end{center}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on real set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-real-set-up-1}{}
\begin{block}{10k simulations (same parameters)}
\protect\hypertarget{k-simulations-same-parameters}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  The 95\% of the data is in range -2.763, 2.698
\item
  21.38\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on real set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-real-set-up-2}{}
\begin{block}{10k simulations with similarity equal to 0.1}
\protect\hypertarget{k-simulations-with-similarity-equal-to-0.1}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  The 95\% of the data is in range 0.851, 2.764
\item
  51.3\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on real set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-real-set-up-3}{}
\begin{block}{10k simulations with similarity equal to 0.4}
\protect\hypertarget{k-simulations-with-similarity-equal-to-0.4}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  The 95\% of the data is in range 1.679, 2.185
\item
  82.9\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}

>>>>

  x11names, dvipsnames, bibspacing,natbib, table]{beamer}

@@

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec}{}
\begin{block}{Question}
\protect\hypertarget{question}{}
How to sensibly represent words with numbers?

\begin{block}{One-hot encoding}
\protect\hypertarget{one-hot-encoding}{}
Well, you could use 30k binary vectors with a slot for each lexical
unit\dots

\dots \dots but this would be inefficient and wouldn't capture any
relations between words.
\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-1}{}
\begin{center}
 \includegraphics[width = 9cm]{images/perceptron1.png}
\end{center}

\vspace{-3mm}

\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}

\begin{block}{Rosenblatt's perceptron}
\begin{itemize}
\item Inputs (pixel intensities) with weights
\item Nodes with activation levels from 0-1
\item (Perhaps) 0-1 output based on a threshold
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-2}{}
\begin{center}
 \includegraphics[width = 9cm]{images/perceptron1.png}
\end{center}

\vspace{-3mm}

\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}

\begin{block}{Learning}
\begin{itemize}
\item Start with random weights
\item Test on a case:
\begin{itemize}
\item If right, don't change weights.
\item If wrong, change weights a bit, with focus on the ones more responsible for the judgment:
\begin{align*}
w_j & \leftarrow w_j = \overbrace{\eta}^{\text{learning rate}}(\underbrace{t}_{\text{correct output}} - \overbrace{y}^{\text{actual output}})\underbrace{x_j}_{\text{actual input}}
\end{align*}
\end{itemize}
\end{itemize}

\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-3}{}
\begin{columns}
\column{0.45\linewidth}

\begin{center}
 \includegraphics[height = 6cm, width = 5cm]{images/perceptron2.png}
\end{center}

\vspace{-3mm}
\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}

\column{0.5\linewidth}

\begin{itemize}
\item Each hidden unit takes a weighted sum of 324 inputs and passes on its activation level as input to outer layer units.

\item Activation levels of outer layers are interpreted as network's levels of confidence in a classification problem.

\item Learning: back-propagation (gradient descent: approximate  the direction of steepest descent in the error surface w.r.t to weights, modify accordingly).
\end{itemize}

\end{columns}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-4}{}
\begin{block}{Distributional semantics}
\protect\hypertarget{distributional-semantics}{}
\begin{itemize}
\item "You shall know a word by the company it keeps" (John Firth, 1957)

\item "the degree of semantic similarity between two linguistic expressions $A$ and $B$ is a function of the similarity of the linguistic contexts in which $A$ and $B$ can appear." (A. Lenci, 2008)

\end{itemize}

\begin{center}
 \includegraphics[height = 5cm, width = 5cm]{images/similarity1.png}
\end{center}

\vspace{-3mm}

\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}
\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-5}{}
\begin{block}{Google and Mikolov}
\protect\hypertarget{google-and-mikolov}{}
\emph{Efficient Estimation of Word Representation in Vector Space}, 2013

Let's train a neural network and use vectors of weights!

\begin{center}
 \includegraphics[height = 5cm, width = 6cm]{images/word2vec1.png}
\end{center}

\vspace{-3mm}

\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}
\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-6}{}
\begin{block}{Google and Mikolov}
\protect\hypertarget{google-and-mikolov-1}{}
\emph{Efficient Estimation of Word Representation in Vector Space}, 2013

Let's train a neural network and use vectors of weights!

\begin{center}
 \includegraphics[height = 3cm, width = 7cm]{images/word2vec2.png}
\end{center}

\vspace{-3mm}

\tiny \hfill \color{gray}Illustration: M. Mitchell \color{black}
\end{block}
\end{frame}

\begin{frame}{Word2vec}
\protect\hypertarget{word2vec-7}{}
\begin{longtable}[]{@{}llllll@{}}
\toprule
word & 1 & 2 & 3 & 4 & \ldots{} \\
\midrule
\endhead
woman & 0.456 & 0.267 & 0.675 & 0.131 & \ldots{} \\
man & 0.451 & 0.897 & 0.472 & 0.088 & \ldots{} \\
\bottomrule
\end{longtable}

\begin{block}{Question}
\protect\hypertarget{question-1}{}
How is this supposed to capture semantic relations?

\begin{block}{General idea}
\protect\hypertarget{general-idea}{}
Similarity in vector direction.
\end{block}
\end{frame}

\begin{frame}{Cosine similarity}
\protect\hypertarget{cosine-similarity}{}
\begin{columns}
\column{0.45\linewidth}

\begin{center}\includegraphics[width=1\linewidth]{presentationBoston_files/figure-beamer/cosine1-1} \end{center}

\column{0.5\linewidth}

\begin{block}{Vectors}
\begin{align*}
a  & = [1,2]\\
b  &= [3,2]
\end{align*}

\end{block}
\pause

\begin{block}{Dot product}

\begin{align*}
a \cdot b & = a_1 b_1 + a_2 b_2\\
a \cdot a & = a_1^2 + a_2 ^ 2 \\
\lVert a\rVert & = \sqrt(a \cdot a)
\end{align*}

\end{block}

\end{columns}
\end{frame}

\begin{frame}{Cosine similarity}
\protect\hypertarget{cosine-similarity-1}{}
\begin{columns}
\column{0.45\linewidth}

\begin{center}\includegraphics[width=1\linewidth]{presentationBoston_files/figure-beamer/cosine2-1} \end{center}

\column{0.5\linewidth}

\begin{block}{Vectors}

\begin{align*}
a  & = [1,2]\\
b  &= [4,4]
\end{align*}

\end{block}

\begin{block}{Dot product}

\begin{align*}
a \cdot b & = a_1 b_1 + a_2 b_2\\
a \cdot a & = a_1^2 + a_2 ^ 2 \\
\lVert a\rVert & = \sqrt(a \cdot a)
\end{align*}

\end{block}

\begin{block}{Vector difference}

\begin{align*}
b - a & = [b_1- a_1, b_2 - a_2 ]
\end{align*}

\end{block}

\end{columns}
\end{frame}

\begin{frame}{Cosine similarity}
\protect\hypertarget{cosine-similarity-2}{}
\begin{columns}
\column{0.45\linewidth}

\begin{center}\includegraphics[width=1\linewidth]{presentationBoston_files/figure-beamer/cosine3-1} \end{center}

\column{0.5\linewidth}

\begin{block}{Vectors}

\begin{align*}
a  & = [1,2]\\
b  &= [4,4]
\end{align*}

\end{block}

\begin{block}{Dot product}

\begin{align*}
a \cdot b & = a_1 b_1 + a_2 b_2\\
a \cdot a & = a_1^2 + a_2 ^ 2 \\
\lVert a\rVert & = \sqrt(a \cdot a)
\end{align*}

\end{block}

\begin{block}{Vector difference}

\begin{align*}
b - a & = [b_1- a_1, b_2 - a_2 ]
\end{align*}

\end{block}

\end{columns}
\end{frame}

\begin{frame}{Cosine similarity}
\protect\hypertarget{cosine-similarity-3}{}
\begin{columns}
\column{0.45\linewidth}

\begin{center}\includegraphics[width=1\linewidth]{presentationBoston_files/figure-beamer/cosine4-1} \end{center}

\column{0.5\linewidth}

\begin{block}{Angle}

\begin{align*}
\lVert b - a \rVert^2 &  = \lVert  b \rVert^2 + \lVert a \rVert^2 - 
  2 \lVert b \rVert   \lvert  a \rVert  \cos \theta  \\
b \cdot a  & = \lVert b\rVert \lVert  a \rVert \cos \theta \\ 
\cos \theta & = \frac{b \cdot a}{\lVert b\rVert  \lVert  a \rVert }
\end{align*}

\end{block}

\begin{block}{Orthogonality}
\begin{align*}
\cos ( 90^{\circ}) & = 0 \\ 
\frac{b \cdot a}{\lVert  b\rVert \lVert a \rVert} & = 0\\ 
 b \cdot a & = 0  
\end{align*}
\end{block}

\end{columns}
\end{frame}

\begin{frame}{Cosine similarity \& distance}
\protect\hypertarget{cosine-similarity-distance}{}
\vspace{-4mm}

\begin{align} \tag{Sim}
\mathsf{cosineSimilarity}(A,B) & = \frac{A \cdot B}{\lVert  A \rVert \,\lVert B \rVert}
\\
\tag{Distance}
\mathsf{cosineDistance}(A,B) &  = 1 - \mathsf{cosineSimilarity}(A,B)
\end{align}

\begin{itemize}
\item
  Geometric interpretation: direction (not length)
\item
  \(\mathsf{cosineDistance}\in (0, 2)\)
\item
  Naive interpretation: proximity corresponds to semantic similarity
\end{itemize}
\end{frame}

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias}{}
\begin{block}{The worry}
\protect\hypertarget{the-worry}{}
Word embeddings can learn implicit harmful biases

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-1}{}
\begin{block}{A visual example}
\protect\hypertarget{a-visual-example}{}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-2}{}
\begin{block}{Example: Word Embedding Association Test (WEAT)}
\protect\hypertarget{example-word-embedding-association-test-weat}{}
\vspace{1mm}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-3}{}
\begin{block}{Example: Word Embedding Association Test (WEAT)}
\protect\hypertarget{example-word-embedding-association-test-weat-1}{}
\begin{align*}
s(t,A,B) & = \frac{\sum_{a\in A}f(t,a)}{\vert A\vert} - \frac{\sum_{b\in B}f(t,b)}{\vert B\vert}
\\
WEAT(A,B) & = \frac{
\mu\left(\{s(x,A,B)\}_{x\in X}\right) -\mu\left(\{s(y,A,B)\}_{y\in Y}\right) 
}{
\sigma\left(\{s(w,A,B)\}_{w\in X\cup Y}\right)
}
\end{align*}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-4}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac}{}
\vspace{1mm}
\footnotesize

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-5}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac-1}{}
\begin{align*}
S(t_i, A_j) & = \frac{1}{\vert A_j\vert}\sum_{a\in A_j}\mathsf{cos}(t,a) \\
MAC(T,A) & = \frac{1}{\vert T \vert \,\vert A\vert}\sum_{t_i \in T }\sum_{A_j \in A} S(t_i,A_j)
\end{align*}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-6}{}
\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}
\protect\hypertarget{our-main-target-mean-average-cosine-similarity-mac-2}{}
\footnotesize 
\begin{table}

@@

\begin{frame}{Cosine-based measures of bias}
\protect\hypertarget{cosine-based-measures-of-bias-7}{}
\begin{block}{General challenges}
\protect\hypertarget{general-challenges}{}
\begin{itemize}
\tightlist
\item
  Gender-direction: insufficient indicator of bias
  \footnotesize  (\protect\hyperlink{ref-Gonen2019lipstick}{Gonen \&
  Goldberg, 2019})
\end{itemize}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems}{}
\begin{block}{Word list choice is unprincipled}
\protect\hypertarget{word-list-choice-is-unprincipled}{}
\begin{itemize}
\tightlist
\item
  We run with it for comparison.
\end{itemize}

@@

\begin{block}{No design considerations to sample size}
\protect\hypertarget{no-design-considerations-to-sample-size}{}
\begin{itemize}
\tightlist
\item
  ETHAYARAJH IS YOUR criticizes WEAT uses Bernstein bounds and argues
  that we would need a bias specific dataset of size at least 11903 to
  claim that the system is biased (three times larger than WinoBias).
\end{itemize}

\begin{itemize}
\tightlist
\item
  We show progress can be made with more sensitive Bayesian methods.
\end{itemize}
\end{block}

\begin{block}{The form of the definition is suspicious}
\protect\hypertarget{the-form-of-the-definition-is-suspicious}{}
ETHAYARAJH UNDERSTANDING shows if there are two target words only WEAT
is always maximal in one direction.

\begin{itemize}
\tightlist
\item
  We show the problem runs deeper and stems from pre-averaging, and we
  statistically gauge the uncertainty that arises from raw sample sizes.
\end{itemize}
\end{block}
\end{frame}

@@

\begin{frame}{Some methodological problems}
\protect\hypertarget{some-methodological-problems-2}{}
\begin{block}{Outliers and surprisingly dissimilar words}
\protect\hypertarget{outliers-and-surprisingly-dissimilar-words}{}
We study those by visualizations and uncertainty estimates.
\end{block}
\end{frame}

@@

\begin{block}{Our simulations}
\protect\hypertarget{our-simulations}{}
Suppose all similarities for two classes are randomly drawn from the
same distribution, \(\mathsf{Normal}(\mu = 0, \sigma = .08)\), you still
can get a really high WEAT!
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging}
\protect\hypertarget{the-problem-with-pre-averaging-1}{}
\begin{block}{Simple case: two pws, four terms}
\protect\hypertarget{simple-case-two-pws-four-terms}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  Raw sd in data is 0.045
\item
  The sd of means is 0.023
\item
  The WEAT score is 1.825\\
\item
  The largest effect size reported by
  \protect\hyperlink{ref-Caliskan2017semanticsBiases}{Caliskan, Bryson,
  \& Narayanan}
  (\protect\hyperlink{ref-Caliskan2017semanticsBiases}{2017}) is 1.81!
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on realistic set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-realistic-set-up}{}
\begin{block}{Simulation with realistic set-up (16 predicates)}
\protect\hypertarget{simulation-with-realistic-set-up-16-predicates}{}
\vspace{1mm}
\footnotesize

\begin{center}\includegraphics[width=0.7\linewidth]{presentationBoston_files/figure-beamer/unnamed-chunk-8-1} \end{center}

Raw sd: 0.082, sd of means: 0.031, WEAT: 2.337.
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on realistic set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-realistic-set-up-1}{}
\begin{block}{10k simulations (same parameters)}
\protect\hypertarget{k-simulations-same-parameters}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  95\% of the scores are in range -2.763, 2.698
\item
  21.38\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on realistic set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-realistic-set-up-2}{}
\begin{block}{10k simulations with mean similarity 0.1}
\protect\hypertarget{k-simulations-with-mean-similarity-0.1}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  95\% of the scores are in range 0.851, 2.764
\item
  51.3\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{The problem with pre-averaging on realistic set-up}
\protect\hypertarget{the-problem-with-pre-averaging-on-realistic-set-up-3}{}
\begin{block}{10k simulations with mean similarity 0.4}
\protect\hypertarget{k-simulations-with-mean-similarity-0.4}{}
\vspace{1mm}
\footnotesize

@@

\begin{itemize}
\tightlist
\item
  95\% of the scores are in range 1.679, 2.185
\item
  82.9\% of the absolute values are above 1.81
\end{itemize}
\end{block}
\end{frame}
